---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r set working directory}
library(data.table); library(dtplyr); library(tidyr); library(tidyverse)
setwd('/Users/alexandradecker/Dropbox/Projects/reactivate/trialorder')
```

Read intentional encoding file; ensure each stimulus is unique
```{r read intentional encoding file}
list.files()
df <- fread("1_intentional_encoding.csv") # this file contains ImageA, ImageB, CategoryB and ImageC

df[, n_distinct(ImageA)]
df[, n_distinct(ImageB)]
df[, n_distinct(ImageC)]
combined_stims <- as.data.table(x = c(df$ImageA, df$ImageB, df$ImageC))
combined_stims[, n_distinct(V1)]
```

For creating a new intentional encoding file
```{r shuffle intentional encoding file}
df[, ImageA := sample(ImageA)]
df[, n_distinct(ImageA)]
rows <- sample(nrow(df)) #shuffle the rows
df <- df[rows,]
df <- df%>%arrange(CategoryB)
df[, ListNum := rep(x  = c(1:4), times = 12)]
df <- df%>%arrange(ListNum)

rows <- sample(nrow(df))
rows1 <- sample(1:12)
rows2 <- sample(13:24)
rows3 <- sample(25:36)
rows4 <- sample(37:48)
rows <- c(rows1, rows2, rows3, rows4)

df <- df[rows,]
df[, Trial:= 1:.N]
df
write.csv(file = "4_intentional_encoding.csv", x = df)
```

Create intentional encoding test file
```{r}
df <- fread("4_intentional_encoding.csv")
df_test_template <- fread("intentional_encoding_test_template.csv")

#check for repeats
df_test_template[, n_distinct(location2)]
df_test_template[, n_distinct(location3)]

combined_stims <- as.data.table(x = c(df$ImageB, df_test_template$location2, df_test_template$location3))
combined_stims[, n_distinct(V1)]
```


Merge intentional encoding file with location 2 and location 3 images
```{r}
# create new test df
dftest_new <- cbind(df_test_template, df[, .(ImageA, location1 = ImageB, CategoryB, correct_image = ImageB, ImageC, ListNum)])
```

Check for repeats in intentional encoding test file
```{r}
dftest_new <- dftest_new[, .(ImageA, location1, location2, location3, CategoryB, correct_image, ImageC, ListNum)]
combined_stims <- as.data.table(x = c(dftest_new$ImageA, dftest_new$location1, dftest_new$location2, dftest_new$location3, dftest_new$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N == 2]
```

Skip this chunk if creating intentional encoding test FINAL
```{r}
#shuffle location 1, 2, and 3
dftest_new[, correct_location := rep(c(1,2,3),4), by = ListNum]
dftest_new[correct_location == 2, `:=` (location2 = location1, location1 = location2)]
dftest_new[correct_location == 3, `:=` (location3 = location1, location1 = location3)]


rows1 <- sample(1:12)
rows2 <- sample(13:24)
rows3 <- sample(25:36)
rows4 <- sample(37:48)
#rows <- sample(1:48)
rows <- c(rows1, rows2, rows3, rows4)
dftest_new <- dftest_new[rows,]
dftest_new[1:12]
dftest_new[, trial := 1:.N]

i <- sample(1:48, size = 1)
dftest_new[trial == i, .(ImageA, correct_image, ImageC, ListNum)]
image <- dftest_new[trial == i, .(ImageA, correct_image, ImageC)]$ImageA
df[ImageA == image, .(ImageA, ImageB, ImageC, ListNum)]


#check repeats again
dftest_new[, n_distinct(ImageA)]
dftest_new[, n_distinct(location1)]
dftest_new[, .N, by = location1]
dftest_new[, n_distinct(location2)]
dftest_new[, n_distinct(location3)]
dftest_new[, n_distinct(ImageC)]

combined_stims <- as.data.table(x = c(dftest_new$ImageA, dftest_new$location1, dftest_new$location2, dftest_new$location3, dftest_new$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N ==2]

write.csv(file = "4_intentional_encoding_test.csv", x = dftest_new)

```


Create final intentional encoding test FINAL
```{r}
#shuffle location 1, 2, and 3
dftest_new[, correct_location := rep(c(1,2,3),16)]
dftest_new[correct_location == 2, `:=` (location2 = location1, location1 = location2)]
dftest_new[correct_location == 3, `:=` (location3 = location1, location1 = location3)]


rows <- sample(1:48)
dftest_new <- dftest_new[rows,]
dftest_new[, trial := 1:.N]

i <- sample(1:48, size = 1)
dftest_new[trial == i, .(ImageA, correct_image, ImageC, ListNum)]
image <- dftest_new[trial == i, .(ImageA, correct_image, ImageC)]$ImageA
df[ImageA == image, .(ImageA, ImageB, ImageC, ListNum)]


#check repeats again
dftest_new[, n_distinct(ImageA)]
dftest_new[, n_distinct(location1)]
dftest_new[, .N, by = location1]
dftest_new[, n_distinct(location2)]
dftest_new[, n_distinct(location3)]
dftest_new[, n_distinct(ImageC)]

combined_stims <- as.data.table(x = c(dftest_new$ImageA, dftest_new$location1, dftest_new$location2, dftest_new$location3, dftest_new$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N ==2]

write.csv(file = "4_intentional_encoding_test_final.csv", x = dftest_new)
```


Make sure two of each for 'old' images (are actually old)
```{r}
list.files()
final_mem <- fread("final_memory_test.csv")
final_mem
final_mem[image_type != "new", ]%>%print(n=Inf)
combined_stims <- as.data.table(x = c(dftest_new$ImageA, dftest_new$ImageC, dftest_new$correct_image, final_mem[image_type != "new"]$Image ))
combined_stims[, .N, by = V1][N==1]
```



check that new images are all actually new
```{r}
list.files()
dftest <- fread("4_intentional_encoding_test.csv")
final_test <- fread("final_memory_test.csv")
names(final_test); names(df_test)
final_test%>%print(n=Inf)

#all images presented at encoding are also presented at retrieval
combined_stims <- as.data.table(x = c(dftest$ImageA, dftest$ImageC, dftest$correct_image, final_test[image_type != "new"]$Image))
combined_stims[, n_distinct(V1), by = V1]
combined_stims[, unique(V1)]


combined_stims <- as.data.table(x = c(dftest$ImageA, dftest$ImageC, dftest$location1, dftest$location2, dftest$location3, final_test$Image))
combined_stims[, n_distinct(V1), by = V1]
combined_stims[, unique(V1)]
```

Check same images across four conditions
```{r}
library(readxl)
list.files()
dftest <- fread("1_intentional_encoding_test.csv")
memory <- as.data.table(read_excel("1_priming_recognition_test.xlsx"))


combined_stims <- as.data.table(x = c(dftest$ImageA, dftest$ImageC, dftest$location1, dftest$location2, dftest$location3, memory[image_type == "new"]$Image))
combined_stims[, unique(V1)]

```


```{r}
combined_stims[, unique(V1)]
names(combined_stims)[1] <- "stimuli"
write.csv(x = combined_stims, file = "to_extract_images.csv")
```

