---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
library(readxl); library(tidyverse); library(data.table); library(dtplyr)
setwd("/Users/alexandradecker/Dropbox/Projects/reactivate/trialorder/")
list.files(pattern = "1_")

intentional <- fread("1_intentional_encoding.csv")
intentional_test <- fread("1_intentional_encoding_test.csv")
intentional_test_final <- fread("1_intentional_encoding_test_final.csv")
abc_test <- as.data.table(read_excel("1_priming_recognition_test.xlsx"))
```

Check images are NOT repeated during incidental encoding task
```{r}
intentional[, n_distinct(ImageA)]
intentional[, n_distinct(ImageB)]
intentional[, n_distinct(ImageC)]

combined_stims <- as.data.table(x = c(intentional$ImageA, intentional$ImageB, intentional$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N ==2]

intentional[ImageA == "images/pants_firefighter.jpg"]
#images are all now unique
```

check that intentional_test encoding test images are unique
```{r}
intentional_test[, n_distinct(ImageA)]
intentional_test[, n_distinct(location1)]
intentional_test[, n_distinct(location2)]
intentional_test[, n_distinct(location3)]
intentional_test[, n_distinct(ImageC)]

combined_stims <- as.data.table(x = c(intentional_test$ImageA, intentional_test$location1, intentional_test$location2, intentional_test$location3, intentional_test$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N ==2]
```


#check new images are really new
```{r}

combined_stims <- as.data.table(x = c(intentional_test$ImageA, intentional_test$ImageB, intentional_test$ImageC))
combined_stims[, n_distinct(V1)]
combined_stims[, .N, by = V1][N ==2]

intentional_test[ImageC == "images/milk_shake.jpg", ImageC := "images/clock_digital.png"]
intentional_test[ImageC == "images/pants_firefighter.jpg", ImageC := "images/clock_digital.png"]
```


Make sure that 'images' is in each cell of each image column
```{r}
#list.files()
#df <- fread("4_intentional_encoding.csv")
#length(grep(pattern  = "images/", x = df$ImageA, value = T))
#length(grep(pattern  = "images/", x = df$ImageB, value = T))
#length(grep(pattern  = "images/", x = df$ImageC, value = T))

df <- fread("4_intentional_encoding_test.csv")
length(grep(pattern  = "images/", x = df$ImageA, value = T))
length(grep(pattern  = "images/", x = df$location1, value = T)) # add images/
length(grep(pattern  = "images/", x = df$location2, value = T)) # add images/
length(grep(pattern  = "images/", x = df$location3, value = T)) # add images/
length(grep(pattern  = "images/", x = df$correct_image, value = T))
length(grep(pattern  = "images/", x = df$ImageC, value = T))

df[!location1 %in% c(grep(pattern  = "images/", x = df$location1, value = T)), location1 := paste0('images/', location1)]
df[location1 %in% c(grep(pattern  = "images/", x = df$location1, value = T)),]

df[!location2 %in% c(grep(pattern  = "images/", x = df$location2, value = T)), location2 := paste0('images/', location2)]
df[location2 %in% c(grep(pattern  = "images/", x = df$location2, value = T)),]

df[!location3 %in% c(grep(pattern  = "images/", x = df$location3, value = T)), location3 := paste0('images/', location3)]
df[location3 %in% c(grep(pattern  = "images/", x = df$location3, value = T)),]

write.csv(file = "4_intentional_encoding_test.csv", x = df)
```

#check that correct locations are randomized across task
```{r}

df <- fread("4_intentional_encoding_test_final.csv")
combined_stims <- as.data.table(x = c(df$ImageA, df$location1, df$location2, df$location3, df$ImageC))
combined_stims[, n_distinct(combined_stims)]

```

Check that new images do not overlap with other image presented already
```{r}
tested_images <- fread("final_memory_test.csv")
#tested_images[!Image %in% c(grep(pattern  = "images/", x = tested_images$Image, value = T))]
#df[!Image %in% c(grep(pattern  = "images/", x = df$Image, value = T))]


combined_stims <- c(combined_stims$V1, tested_images[image_type == 'new']$Image)
stimuli <- as.data.table(x = combined_stims)
stimuli[, n_distinct(combined_stims)]


tested_images[, .N, by = Image][N ==2]
tested_images[, n_distinct(Image)]
```


#check location correct is correct!
```{r}
df <- fread("4_intentional_encoding_test_final.csv")
df[, .N, by= correct_location]
```

